---
title: "Journal (reproducible report)"
author: "Jonathan Zorn"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include= FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Intro

As I am not quite sure how we are supposed to structure the journal, i will focus on the bigger Exercises and the challanges. The smaller Exercises can be seen below.

# Tidyvers

Last compiled: `r Sys.Date()`

## Challenge

```{r, eval=TRUE}
# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS ----

# 1.0 Load libraries ----
library(tidyverse)
library(readxl)

# 2.0 Importing Files ----
bikes_tbl <- read_excel(path = "00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl  <- read_excel("00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")

# 4.0 Joining Data ----
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
bike_orderlines_joined_tbl %>% glimpse()
# 5.0 Wrangling Data ----
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ", ") %>%
  mutate(total.price = price * quantity) %>%
  select(-...1, -gender) %>%
  select(order.id, contains("order"), contains("state"), contains("city"),
         price, quantity, total.price,
         everything()) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))
# 6.0 Business Insights ----

# 6.1 Sales by Year ----

library(lubridate)
# Step 1 - Manipulate
sales_by_loc_tbl <- bike_orderlines_wrangled_tbl %>%
  # Select columns
  select(state, total_price) %>%
  # Grouping by year and summarizing sales
  group_by(state) %>% 
  summarize(sales = sum(total_price)) %>%
  # Optional: Add a column that turns the numbers into a currency format 
  # (makes it in the plot optically more appealing)
  # mutate(sales_text = scales::dollar(sales)) <- Works for dollar values
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_loc_tbl
# 6.1 Sales by Year ----
```

```{r plot, fig.width=25, fig.height=10}
# Step 2 - Visualize
sales_by_loc_tbl %>%
  
  # Setup canvas with the columns year (x-axis) and sales (y-axis)
  ggplot(aes(x = state, y = sales)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  
  # Geometries
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
 # geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  
  
  # Formatting
  # scale_y_continuous(labels = scales::dollar) + # Change the y-axis. 
  # Again, we have to adjust it for euro values
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by state",
    x = "State", # Override defaults for x and y
    y = "Revenue"
  )

```

```{r, eval=TRUE}
# 6.2 Sales by Year and Category 2 ----
# Step 1 - Manipulate
sales_by_year_loc_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns and add a year
  select(order_date, total_price, state) %>%
  mutate(year = year(order_date)) %>%
  
  # Group by and summarize year and main catgegory
  group_by(year, state) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  
  # Format $ Text
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_year_loc_tbl 
```

```{r plot1, fig.width=10, fig.height=10}
# Step 2 - Visualize
sales_by_year_loc_tbl %>%
  
  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = state)) +
  
  # Geometries
  geom_col() + # Run up to here to get a stacked bar plot
  
  # Facet
  facet_wrap(~ state) +
  
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and state",
    subtitle = "Each product category has an upward trend",
    fill = "State" # Changes the legend name
  )
```
Save again and overwrite, not sure how we are supposed to handle that but to be on the save side:
```{r, eval = FALSE}
# 7.0 Writing Files ----
# 7.1 Excel ----
#install.packages("writexl")
library("writexl")
bike_orderlines_wrangled_tbl %>%
  write_xlsx("00_data/01_bike_sales/02_wrangled_data/bike_orderlines.xlsx")

# 7.2 CSV ----
bike_orderlines_wrangled_tbl %>% 
  write_csv("00_data/01_bike_sales/02_wrangled_data/bike_orderlines.csv")

# 7.3 RDS ----
bike_orderlines_wrangled_tbl %>% 
  write_rds("00_data/01_bike_sales/02_wrangled_data/bike_orderlines.rds")

```

# Data Aquisition
## Challenge2.1
Here I will get some weather Data:

```{r, eval = TRUE}
library(tidyverse)
library(httr)
library(glue)


api_key <- "00983b00961d78e6db02be765c604c7b"
base_url <- "https://api.openweathermap.org/data/2.5/weather"


city_list <- c("Hamburg","Bonn","Berlin")
weather_tbl <- tibble(City = character() ,Temperature = numeric())
for (city in city_list) {
  weather_path <- "?q={city}&appid={api_key}"
  api_url <- glue(base_url, weather_path)
  weather <- GET(url = api_url)
  weather_data <- weather %>% content(as = 'parsed')
  temperature <-  weather_data$main$temp - 273.16
  weather_tbl <- weather_tbl %>% add_row(City = city, Temperature = temperature)
  weather_tbl
}

```

## Challenge 2.2
Here I will get the name and Price of all Rose Bikes

```{r, eval = TRUE}
library(tidyverse)
library(rvest)     
library(glue)
library(stringr)
library(purrr)

base_url <- "https://www.rosebikes.de"
bike_path <- "fahrräder"

bike_url <- glue(base_url, "/",bike_path)
bike_html <- bike_url %>% read_html()

category_path <- bike_html %>% html_nodes(css = ".catalog-navigation__list-item > a") %>% html_attr("href") %>% discard(.p = ~stringr::str_detect(.x,"zoovu|sale" ))  %>% enframe(value = "Path")
categorys <- category_path %>%  mutate(category = category_path$Path %>% map( str_extract,"(?<=./).+"))
i = 1
for (category in categorys$category) {
  categorys$category[[i]] <- glue(bike_url,"/", category)
  i <- i+1
}

category_html <- categorys$category %>% map(read_html)
bike_name <- category_html %>% map(html_nodes, css = c(".catalog-category-bikes__title-text") ) %>%  map(html_text) %>% enframe(value = "Name")
bike_price <- category_html %>% map(html_nodes, css = c(".catalog-category-bikes__price-title") ) %>%  map(html_text) %>% enframe(value = "Price")
bike_info <- merge(bike_name,bike_price)
bike_info <- bike_info %>% mutate(Name_str = map(.$Name, toString) %>% str_remove_all("[\"c()]|\\n")) %>% 
  mutate(Price_str = map(.$Price, toString) %>% str_remove_all("[\"c()]|\\n|ab "))
bike_info_name <- strsplit(bike_info$Name_str, split = ", ") %>% unlist() %>% enframe(value = "Name")
bike_info_price <- strsplit(bike_info$Price_str, split = ", ") %>% unlist() %>% enframe(value = "Price")
bike_info <- merge(bike_info_name, bike_info_price)

  
```



# Exercise
Here is will just document the Exercises in case that is relevant for the class.

## tidyverse

```{r, eval = FALSE}

D <- 1000
K <- 5
h <- 0.25
die <-1:6
Q=sqrt((2*D*K)/h)
car <- mtcars
Q
K
h
die
history()
mean(die)
round(mean(die), digits = 2)
dice <- sample(die, size = 2, replace = TRUE)
dice
## 3 4

sum(dice)
## 7
roll <- function() {
  die <- 1:6
  dice <- sample(die, size = 2, replace = TRUE)
  sum(dice)
}
roll()
roll2 <- function(faces = 1:6) {
  dice <- sample(faces, size = 2, replace = TRUE)
  sum(dice)
}

roll2()
## 9
roll2(faces = 1:6)
## 7

roll2(faces = 1:10)
## 13
roll3 <- function(faces = 1:6, num_of_dice = 2) {
  dice <- sample(faces, size = num_of_dice, replace = TRUE)
  sum(dice)
}

roll3(faces = 1:6, num_of_dice = 3)
tibble(
  x = 1:50,
  y = runif(50), 
  z = x + y^2,
  outcome = rnorm(50)
)

class(cars)
## "data.frame"

cars_tbl <- as_tibble(cars)
class(cars_tbl)
## "tbl_df"     "tbl"        "data.frame"


# This way applies to dataframes and tibbles
vehicles <- as_tibble(cars[1:5,])
vehicles[['speed']]
vehicles[[1]]
vehicles$speed

# Using placeholders with the pipe
vehicles %>% .$dist
vehicles %>% .[['dist']]
vehicles %>% .[[2]]

library(tidyverse)
diamonds2 <- readRDS("Data/diamonds2.rds")
diamonds2 %>% head(n = 5)

diamonds2 %>%  pivot_longer(cols      = c("2008", "2009"), 
               names_to  = 'year', 
               values_to = 'price') %>% 
  head(n = 5)

diamonds3 <- readRDS("Data/diamonds3.rds")

diamonds3 %>% head(n = 5)

diamonds3 %>% 
  pivot_wider(names_from  = "dimension",
              values_from = "measurement") %>% 
  head(n = 5)

diamonds4 <- readRDS("Data/diamonds4.rds")

diamonds4

diamonds4 %>% 
  separate(col = dim,
           into = c("x", "y", "z"),
           sep = "/",
           convert = T)
diamonds5 <- readRDS("Data/diamonds5.rds")

diamonds5

diamonds5 %>% 
  unite(clarity, clarity_prefix, clarity_suffix, sep = '')

library(ggplot2) # To load the diamonds dataset
library(dplyr)
diamonds %>% 
    filter(cut == 'Ideal' | cut == 'Premium', carat >= 0.23) %>% 
    head(5)

diamonds %>% 
   filter(cut == 'Ideal' | cut == 'Premium', carat >= 0.23) %>% 
   slice(3:4)

diamonds %>% 
  arrange(cut, carat, desc(price))

diamonds %>% 
  select(color, clarity, x:z) %>% 
  head(n = 5)

diamonds %>% 
  select(-(x:z)) %>% 
  head(n = 5)

diamonds %>% 
  select(x:z, everything()) %>% 
  head(n = 5)

diamonds %>% 
  rename(var_x = x) %>% 
  head(n = 5)

diamonds %>% 
  mutate(p = x + z, q = p + y) %>% 
  select(-(depth:price)) %>% 
  head(n = 5)

diamonds %>% 
  transmute(carat, cut, sum = x + y + z) %>% 
  head(n = 5)

diamonds %>% 
  group_by(cut) %>% 
  summarize(max_price  = max(price),
            mean_price = mean(price),
            min_price  = min(price))

glimpse(diamonds)

library(lubridate)
ymd(20101215)

mdy("4/1/17")


bday <- dmy("14/10/1979")
month(bday)
year(bday)



con <- RSQLite::dbConnect(drv    = SQLite(), 
                          dbname = "00_data/02_chinook/Chinook_Sqlite.sqlite")
dbListTables(con)
tbl(con, "Album")
album_tbl <- tbl(con, "Album") %>% collect()
x <- dbGetQuery(con, 'SELECT * FROM Artist')
dbDisconnect(con)
con
resp <- GET("https://swapi.dev/api/people/1/")
sw_api <- function(path) {
  url <- modify_url(url = "https://swapi.dev", path = glue("/api{path}"))
  resp <- GET(url)
  stop_for_status(resp) # automatically throws an error if a request did not succeed
}
resp <- sw_api("/people/1")
resp
rawToChar(resp$content)
list_of_skywalker <- fromJSON(rawToChar(resp$content))
data_list <- list(strings= c("string1", "string2"), 
                  numbers = c(1,2,3), 
                  TRUE, 
                  100.23, 
                  tibble(
                    A = c(1,2), 
                    B = c("x", "y")
                  )
)
resp %>% 
  .$content %>% 
  rawToChar() %>% 
  fromJSON()
content(resp, as = "parsed")
token    <- "HVMLJJRJLDJXBO7C"
response <- GET(glue("https://www.alphavantage.co/query?function=GLOBAL_QUOTE&symbol=WDI.DE&apikey={token}"))
response
alphavantage_api_url <- "https://www.alphavantage.co/query"
ticker               <- "WDI.DE"


```

```{r, eval=FALSE}
# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS ----

# 1.0 Load libraries ----
library(tidyverse)
library(readxl)

# 2.0 Importing Files ----
bikes_tbl <- read_excel(path = "00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl  <- read_excel("00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")
# 3.0 Examining Data ----
orderlines_tbl
glimpse(bikes_tbl)

# 4.0 Joining Data ----
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
bike_orderlines_joined_tbl %>% glimpse()
# 5.0 Wrangling Data ----
bike_orderlines_joined_tbl %>% 
  select(category) %>%
  filter(str_detect(category, "^Mountain")) %>% 
  unique()

bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  mutate(total.price = price * quantity) %>%
  select(-...1, -gender) %>%
  select(-ends_with(".id")) %>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))
glimpse(bike_orderlines_wrangled_tbl)

# 6.0 Business Insights ----

# 6.1 Sales by Year ----

library(lubridate)
# Step 1 - Manipulate
sales_by_year_tbl <- bike_orderlines_wrangled_tbl %>%
  # Select columns
  select(order_date, total_price) %>%
  # Add year column
  mutate(year = year(order_date)) %>%
  # Grouping by year and summarizing sales
  group_by(year) %>% 
  summarize(sales = sum(total_price)) %>%
  # Optional: Add a column that turns the numbers into a currency format 
  # (makes it in the plot optically more appealing)
  # mutate(sales_text = scales::dollar(sales)) <- Works for dollar values
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_year_tbl
# 6.1 Sales by Year ----

# Step 2 - Visualize
sales_by_year_tbl %>%
  
  # Setup canvas with the columns year (x-axis) and sales (y-axis)
  ggplot(aes(x = year, y = sales)) +
  
  # Geometries
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  
  # Formatting
  # scale_y_continuous(labels = scales::dollar) + # Change the y-axis. 
  # Again, we have to adjust it for euro values
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by year",
    subtitle = "Upward Trend",
    x = "Year", # Override defaults for x and y
    y = "Revenue"
  )

# 6.2 Sales by Year and Category 2 ----
# Step 1 - Manipulate
sales_by_year_cat_1_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns and add a year
  select(order_date, total_price, category_1) %>%
  mutate(year = year(order_date)) %>%
  
  # Group by and summarize year and main catgegory
  group_by(year, category_1) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  
  # Format $ Text
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_year_cat_1_tbl 

# Step 2 - Visualize
sales_by_year_cat_1_tbl %>%
  
  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = category_1)) +
  
  # Geometries
  geom_col() + # Run up to here to get a stacked bar plot
  
  # Facet
  facet_wrap(~ category_1) +
  
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and main category",
    subtitle = "Each product category has an upward trend",
    fill = "Main category" # Changes the legend name
  )
```

























